%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Xiaozhi Liu - Modern Tech Industry CV
% Clean, ATS-Friendly, Minimalist Design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font popular in tech

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Xiaozhi Liu} \\ \vspace{8pt}
    \small
    \raisebox{-0.1\height}\faPhone\ (+86) 135-9300-4230 ~
    \href{mailto:xzliu@buaa.edu.cn}{\raisebox{-0.2\height}\faEnvelope\ \underline{xzliu@buaa.edu.cn}} ~
    \href{https://xzliu-opt.github.io/}{\raisebox{-0.2\height}\faGlobe\ \underline{xzliu-opt.github.io}} ~
    \href{https://github.com/xzliu-opt}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/xzliu-opt}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Beihang University}{Beijing, China}
      {Ph.D. in Applied Mathematics, \textbf{GPA: 91.45/100 (Rank: 4/27)}}{Sept. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{School of Mathematical Sciences \& \textbf{Shen Yuan Honors College} (Top 35 students university-wide)}
        \resumeItem{Supervisor: Prof. Yong Xia}
      \resumeItemListEnd

    \resumeSubheading
      {Northwestern Polytechnical University}{Xi'an, China}
      {B.S. in Information \& Computing Science, \textbf{GPA: 88.01/100 (Rank: 4/43)}}{Sept. 2018 -- Jul. 2022}
      \resumeItemListStart
        \resumeItem{Achieved GPA of \textbf{97.89/100} during junior year, ranking \textbf{1st in entire college (1/104)}}
        \resumeItem{Supervisor: Prof. Jianchao Bai}
      \resumeItemListEnd

    \resumeSubheading
      {Université catholique de Louvain}{Louvain-la-Neuve, Belgium}
      {Visiting Ph.D. in Applied Mathematics, \textbf{Funded by China Scholarship Council (CSC)}}{Oct. 2025 -- Oct. 2026}
      \resumeItemListStart
        \resumeItem{INMA/ICTEAM | Supervisor: Prof. Geovani N. Grapiglia}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-12pt}

%-----------RESEARCH INTERESTS-----------
\section{Research Interests}
    \small{Optimization theory and algorithms, with applications in \textbf{signal processing} and \textbf{wireless communications}. Focus on developing efficient algorithms for large-scale optimization problems in 5G/6G MIMO systems and machine learning.}
\vspace{-8pt}

%-----------PUBLICATIONS-----------
\section{Publications \& Preprints}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{A Unified Algorithmic Framework for Dynamic Compressive Sensing}}{2025}
          \resumeItemListStart
            \resumeItem{\textbf{Xiaozhi Liu}, Yong Xia. \textit{Signal Processing: 232, 109926.} [\href{https://github.com/xzliu-opt}{GitHub}]}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Cubic NK-SVD: Parametric Dictionary Design in Frequency Estimation}}{2025}
          \resumeItemListStart
            \resumeItem{\textbf{Xiaozhi Liu}, Yong Xia. \textit{Signal Processing: 235, 110029.} [\href{https://github.com/xzliu-opt}{GitHub}]}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Split-Merge: A Difference-based Approach for Dominant Eigenvalue Problem}}{2025}
          \resumeItemListStart
            \resumeItem{\textbf{Xiaozhi Liu}, Yong Xia. \textit{arXiv: 2501.15131.}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Split-Merge Revisited: Scalable Generalized Eigenvalue Problems}}{2025}
          \resumeItemListStart
            \resumeItem{\textbf{Xiaozhi Liu}, Yong Xia. \textit{arXiv: 2507.02389.}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Revisiting Atomic Norm Minimization: Sequential Atom Identification}}{2024}
          \resumeItemListStart
            \resumeItem{\textbf{Xiaozhi Liu}$^*$, Jinjiang Wei$^*$, Yong Xia. \textit{arXiv: 2411.08459.}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Key R\&D Program of China}{Sept. 2022 -- Present}
      {Core Technical Member | 5.5G Massive MIMO Parameter Estimation}{Beihang University}
      \resumeItemListStart
        \resumeItem{Developed novel algorithms for channel state information (CSI) estimation in 5.5G Massive MIMO systems}
        \resumeItem{Optimized hybrid beamforming (HBF) algorithms, improving spectral efficiency by 30\%}
        \resumeItem{Implemented super-resolution parameter estimation techniques using compressive sensing and optimization}
        \resumeItem{Published 2 papers in \textit{Signal Processing} journal (IF: 4.4, Q1)}
      \resumeItemListEnd

    \resumeSubheading
      {ASC International Student Supercomputer Challenge}{Nov. 2020 -- Jan. 2021}
      {Project Leader | BERT Model for NLP Cloze Tests}{\textbf{Second Prize}}
      \resumeItemListStart
        \resumeItem{Led team to implement and optimize BERT model under PyTorch framework from scratch}
        \resumeItem{Achieved 85\%+ accuracy on CLOTH dataset through fine-tuning and hyperparameter optimization}
        \resumeItem{Leveraged GPU parallel computing on Linux HPC platform, reducing training time by 60\%}
        \resumeItem{Designed efficient data pipeline for large-scale NLP dataset processing}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hong Kong Baptist University}{Aug. 2025 -- Sep. 2025}
      {Research Assistant | LLM Fine-tuning Optimization}{Hong Kong, China}
      \resumeItemListStart
        \resumeItem{Improved LoRA-based parameter-efficient fine-tuning (PEFT) strategies for large language models}
        \resumeItem{Reduced fine-tuning parameters by 40\% while maintaining model performance}
        \resumeItem{Collaborated with Prof. Michael K. Ng (SIAM Fellow) and Prof. Guangning Xu}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------HONORS & AWARDS-----------
\section{Honors \& Awards}
    \begin{multicols}{2}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{National Scholarship} (Ph.D., Top 0.2\%) \hfill 2025 \\
         \textbf{National Scholarship} (B.S., Top 0.2\%) \hfill 2021 \\
         \textbf{Ph.D. Freshman Scholarship} (Top 3/College) \hfill 2022 \\
         \textbf{Outstanding Graduate} \hfill 2022 \\
         \textbf{1st Prize}, National Math Competition \hfill 2020 \\
         \textbf{1st Prize}, Math Contest in Modelling \hfill 2020 \\
        }}
    \end{itemize}
    \end{multicols}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, MATLAB, C, Julia, LaTeX} \\
     \textbf{ML/DL Frameworks}{: PyTorch, TensorFlow, scikit-learn, NumPy, Pandas} \\
     \textbf{Tools \& Platforms}{: Git, Linux, Docker, Jupyter, VS Code} \\
     \textbf{High Performance Computing}{: CUDA, GPU Programming, Parallel Computing} \\
     \textbf{Languages}{: English (Fluent - CET-4: 593, CET-6: 523, PETS-5), Mandarin (Native)} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------CONFERENCE PRESENTATIONS-----------
\section{Conference Presentations}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {21st Annual Meeting of CSIAM}{Oct. 12-15, 2023}
        \resumeItemListStart
          \resumeItem{\textit{A Unified Algorithmic Framework for Dynamic Compressive Sensing}, Kunming, Yunnan}
        \resumeItemListEnd
    \resumeProjectHeading
        {1st ORSC Conference on Data Science and OR Intelligence}{Sep. 13-15, 2024}
        \resumeItemListStart
          \resumeItem{\textit{Cubic NK-SVD: An Algorithm for Designing Parametric Dictionary}, Beijing}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
